Who's Homeless in Toronto: Major Trends in Single Adults Aged 25 to 44 Becoming Homeless from 2018 to 2024

### 2024-09-27 paper/paper.qmd
use styler on the paper.qmd and update paper.pdf

# Calculate percentages
single_adult_population <- single_adult_population %>%
  mutate(
    percentage = total_population / sum(total_population) * 100,
    label = paste0(round(percentage, 1), "%")
  ) # Create a label with percentage

# Plot the pie chart
ggplot(single_adult_population, aes(x = "", y = percentage, fill = `Age Group`)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = label), position = position_stack(vjust = 0.5)) + # Add percentage labels
  theme_void() + # Remove unnecessary axes
  theme(legend.position = "right") +
  scale_fill_brewer(palette = "Set3") # Optional: Add color palette
```
@fig-age-group-distribution-single-adult-pie shows the distribution of age groups within the current single adult homeless population, highlighting the predominance of the 25.34 and 35.44 year old age groups, which account for approximately 25.2% and 25.8% of the total population respectively. In contrast, the 16.24 year old age group is relatively underrepresented at 8.5%. 65 years and over are not represented in any of the single adult populations, accounting for 0%. The under-16s are minors and therefore account for 0%. This distribution suggests that middle-aged people form the bulk of the population, while the young and the old are virtually absent.
```{r}
#| echo: false
#| warning: false
#| label: fig-age-group-proportion-trend-yearly
#| fig-cap: "Trends in Age Group Proportions Over Time (Yearly)"

>>>>

# Calculate percentages and filter out zero percentages
single_adult_population <- single_adult_population %>%
  mutate(
    percentage = total_population / sum(total_population) * 100,
    label = paste0(round(percentage, 1), "%")
  ) %>%
  filter(percentage > 0) # Exclude rows where percentage is 0

# Plot the pie chart
ggplot(single_adult_population, aes(x = "", y = percentage, fill = `Age Group`)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = label), position = position_stack(vjust = 0.5)) + # Add percentage labels
  theme_void() + # Remove unnecessary axes
  theme(legend.position = "right") +
  scale_fill_brewer(palette = "Set3") # Optional: Add color palette

```
@fig-age-group-distribution-single-adult-pie shows the distribution of age groups within the current single adult homeless population, highlighting the predominance of the 25.34 and 35.44 year old age groups, which account for approximately 25.2% and 25.8% of the total population respectively. In contrast, the 16.24 year old age group is relatively underrepresented at 8.5%. 65 years and over are not represented in any of the single adult populations, accounting for 0%. The under-16s are minors and therefore account for 0%. This distribution suggests that middle-aged people form the bulk of the population, while the young and the old are virtually absent.
```{r}
#| echo: false
#| warning: false
#| label: fig-age-group-proportion-trend-yearly
#| fig-cap: "Trends in Age Group Proportions Over Time (Yearly)"
